\documentclass[12pt,letterpaper]{article}


\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
\usepackage{listings}
\usepackage[colorlinks=true,pagebackref,linkcolor=blue]{hyperref}

\theoremstyle{definition}
\newtheorem{dfn}{Definition}

\begin{document}

% The numbers below controls the amount of space between the following sections
\def\shiftdowna{0.32in}  % Adjust for balance
\def\shiftdownb{0.22in}  % Adjust for balance

% Set up the boiler plate at the top of the page

\begin{center}
\textbf{{\large Health Care Project Work Statement}}\\


% SPONSOR
\vspace \shiftdowna
\underline {Sponsored: HUMANA INC. INFUSION PROGRAM }\\ 
\vspace{5pt}
\textbf{{\large The Humana.Inc}}\\


% TITLE
\vspace \shiftdowna
\textbf{{\large Analysis and Introduce of Foreign Policy in Health Care }}


% STUDENTS
\vspace{0.35in}
\vspace \shiftdownb
\underline {Participants} \\
\vspace{5pt}
\text{Hua Hua}, \texttt{hhua1@jhu.edu}

% SPONSORS
\vspace \shiftdownb
\underline {Potential Participants}\\
\vspace{5pt}
Tianyu Luo, \texttt{luoty07@gmail.com} \\
\vspace{3pt}
\text{Zichan Wang}, \texttt{zichan.wang@gmail.com} \\
\vspace{3pt}
\text{}, \texttt{}

% DATE
\vspace \shiftdowna
Date: \today

\end{center}

\vfill  
%Fill page to force following note to bottom
\footnoterule
\noindent \small{Any apparent association of this work to The Humana.Inc is
fictional one, and the sole purpose of this work is a class exercise}

\newpage

\section{Introduction and Background} 
Humana Inc. is a leading health care provider headquartered in Louisville, Kentucky. Humana is developing this infusion program to sponsorship research projects that aim to improve the efficiency and research new solutions to this industry. The health care system in United State is under great pressure. The system is high in cost, but the results in term of customer satisfactory are very poor. New solutions are needed to bring talent ideals and people into the challenge.Humana.Inc is aim to inspire that guides us to meaningful activities that bring joy to our lives; to presents of the meaningful relationships in your life and connections within community; to feel of being safe and the assurance that you are protected and to have the energy, physical freedom and desire to thrive in living every day

\section{Problem Statement}

Colorectal cancer (CRC) screening is a very effective method in earlier cancer decetion. Increase the participating rate of population attend this screening will lower the health cost and survival rate of the cancer. Through a questionare survery data conducted in a commuity population in urban China, this project is aimed to find the cause of the low particifation rate and formulate a suitable public health policy to increase the participation rate.  

\section{Approach Method} 
Using contronl group that match the person who attend the CRC screeing with age, gender, eucation level ...ect.

Control 1: included those having a positive test results but refusing a CRC. 

Control 2: included those who refused both positive test results and CRC.

Investigate the correclation between those parameter and the participation rate. After the data analysis, in term of the policy, the corresponding solution such as: 1.Raising the public awarenes 2.Painless CRC method needed to be developped 3.Government subsidized the cost of CRC.
The data analysis in the end of the project should be able to provice the reasioning of choseing the most effective public policy.

\section{Work Flow Chart}
The period of performance for the project is beginning on 10/01/2012 through 12/01/2012. All the research will be completed within this timeframe. The final report and presentation will be delivered. Any modifications or extensions will not be allowed.

Below listed major milestones of project’s different stage. Project will be expected to performing tasks throughout various stages of this project.  The following is a list of these tasks which will result in the successful completion of this project:


\underline {Kichoff:}
\begin{itemize}
    \item Literature research, selection of successful public health policies
    \item Analysis on different policies and chose the best candidates
\end{itemize}




\underline {Design Phase:}
\begin{itemize}
    \item Develop the model to quantify the results of the polies 
    \item Doing regression analysis on categorical analysis on different parameter: sex, gender, race, income level, education level
   \item Modify and finalize the model
    \item Present formal report on the model and model validation
\end{itemize}

\underline {Apply Phase:}
\begin{itemize}
    \item Acquire sample or national data of specified region for analysis
    \item Acquire data and use the model to generated results according to the data
    \item Model modification and policies modification to generate reasonable and better performance
    \item Present formal public policies case backed with modeling results
\end{itemize}

 
\underline {Project Closure:}
\begin{itemize}
    \item Formal report of a public policy consulting report
    \item Presentation of the project. 
\end{itemize}

 
\section{Milestones}
Proposed deadlines for specific project tasks:
\begin{itemize}
    \item Work Statement due date, Oct 16, 2012,
    \item Midterm Presentation due date, Oct 17, 2012,
    \item Progress Report due date, Oct 26, 2012,
    \item Final Presentation due date, Nov 6, 2012,
    \item Final Report due date, Nov 30, 2012.
\end{itemize}

\section{Deliverable}
\subsection{From Team to Sponsor} % (fold)
The following outputs are expected from this project:
\begin{itemize}
    \item regressional analysis of the data on the questionaire survery data. 
        Certain correctlation relationships between the variables in the survery will be suggested 
    \item Completed model. Model that able to predict the participating rate of CRC in term of revelent varibales.
    \item Validation of the model using a different population set. 
    \item Corresponding effective public health policy will be provided according to the model claim
    \item Technical report and presentations summarizing the work. 
\end{itemize}

\subsection{From Sponsor to Team} % (fold)

In order for our project to be of successful one, we will need:
\begin{itemize}
    \item Sponsor have no obligation to the research team during the project cycles.
\end{itemize}

\section{Reference}
\bibliographystyle{plain}
\nocite{*}
\bibliography{biblioWS}

\end{document}
